Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Fix a bad LaTeX line break.

%As depicted in Figure~\ref{fig:nell},
Nell's characters are
always-available agents layered above a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switching activities; jumping into a
related story module/lesson plan).

>>>>

%As depicted in Figure~\ref{fig:nell},
Nell's characters are
always-available agents layered above a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switching activities; jumping into a
related story module).
